---
title: "R Regression tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

## Chapter 1

```{r, exercise = F, include = F}
library(readr)
height_weight <- read_csv("https://statisticsbyjim.com/wp-content/uploads/2019/01/HeightWeight.csv") 
plot(height_weight, xlab = 'Height M', ylab = 'Weight kg', pch = 19, col = 'royalblue')
```

Start by importing the data. The `readr` package will import the `read_csv` function, allowing us to pull in the csv from the webpage.
```{r import_data, exercise = TRUE, message = F}
library(readr)
height_weight <- read_csv("https://statisticsbyjim.com/wp-content/uploads/2019/01/HeightWeight.csv") 
```

To look at the data, we can use the `head` function.
```{r head_height_weight, exercise = TRUE}
head(height_weight)
```

Update the previous function to see the first 8 rows of data.
```{r head_8_height_weight, exercise = TRUE, exercise.lines= 2}

```

<div id="head_8_height_weight-hint">
**Hint:** For help on this function, try `help(head)` or `?head`.
</div>

Next we'll plot the `Height` and `Weight` variables.
```{r plot_height_weight, exercise = T}
plot(height_weight,        # basic plot command
  xlab = 'Height M',       # labels x axis
  ylab = 'Weight kg',      # labels y axis
  pch = 19,                # makes circles solid
  col = 'royalblue')       # sets color
```

Next we'll get the correlation between height and weight, as well run a hypothesis test of the correlation.

There are a variety of ways to select columns. We're using `<data.frame>$<variable name>`. We have to put the variable name in single quotes because there is a space in the name.
```{r}
cor(height_weight$`Height M`, height_weight$`Weight kg`)
cor.test(height_weight$`Height M`, height_weight$`Weight kg`)$p.value
```


Used this [function](https://stats.stackexchange.com/questions/83172/generate-two-variables-with-precise-pre-specified-correlation)

```{r}
library('MASS')
cor_sim <- function(r = 1.0){
  samples = 200
  data = mvrnorm(n=samples, mu=c(0, 0), Sigma=matrix(c(1, r, r, 1), nrow=2), empirical=TRUE)
  x = data[, 1]  # standard normal (mu=0, sd=1)
  y = data[, 2]  # standard normal (mu=0, sd=1)
  plot(x,y, main = paste('Correlation =',round(r,2)), pch = 19, col = 'royalblue')
}
```

```{r}
cor_sim(1.0)
```

```{r}
cor_sim(0.8)
```

```{r}
cor_sim(.6)
```

```{r}
cor_sim(0)
```

```{r}
cor_sim(-1.0)
```

```{r}
cor_sim(-.8)
```

```{r}
cor_sim(-.6)
```

```{r}
x = rnorm(20)
y = x^2 + rnorm(20)/10
cor(x,y)
plot(x,y)
abline(lm(y~x))
#lines(x,predict(lm(y~x + x^2)), col = 'red', lty = 3)
```
